### 2017-05-29 paper.tex
Affiliations
Updated Damien's affiliation

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Collaborative Lesson Development}
}
\newline
\\
{Gabriel~A.~Devenyi}\textsuperscript{1},
{R\'{e}mi~Emonet}\textsuperscript{2},
{Rayna~M.~Harris}\textsuperscript{3},
{Kate~Hertweck}\textsuperscript{4},
{Damien~Irving}\textsuperscript{5},
{Ian~Milligan}\textsuperscript{6},
{Greg~Wilson}\textsuperscript{7, *}
\\
\textbf{1} Douglas Mental Health University Institute / FIXME \\
\textbf{2} FIXME: affiliation and email \\
\textbf{3} University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO / FIXME \\
\textbf{6} University of Waterloo / FIXME email \\
\textbf{7} Rangle.io / gvwilson@third-bit.com
\\
* Corresponding author.
\end{flushleft}

>>>>

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Collaborative Lesson Development}
}
\newline
\\
{Gabriel~A.~Devenyi}\textsuperscript{1},
{R\'{e}mi~Emonet}\textsuperscript{2},
{Rayna~M.~Harris}\textsuperscript{3},
{Kate~Hertweck}\textsuperscript{4},
{Damien~Irving}\textsuperscript{5},
{Ian~Milligan}\textsuperscript{6},
{Greg~Wilson}\textsuperscript{7, *}
\\
\textbf{1} Douglas Mental Health University Institute / gdevenyi@gmail.com \\
\textbf{2} Universit\'{e} Jean Monnet / remi.emonet@univ-st-etienne.fr \\
\textbf{3} University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} Rangle.io / gvwilson@third-bit.com
\\
* Corresponding author.
\end{flushleft}
